---
title: "Isochrone"
author: "Leonard-Allen"
Last Update: 7/05/2022
output:
  html_document:
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: yes
    theme: readable
  pdf_document:
    toc: yes
    toc_depth: '4'
colorlinks: yes
urlcolor: blue
linkcolor: blue
citecolor: blue
anchorcolor: blue
toccolor: blue
fontsize: 12pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Loading my packages

```{r}
#setwd("C:/Users/Leo Allen/Desktop/Isochrones/isochrones")  #set the working directory

library(RColorBrewer)
library(traveltime)
library(tidyverse)
library(tidycensus)
library(sf)
library(osmdata)
library(leaflet)
library(sp)
library(purrr)
library(mapview)
library(osrm)
library(rmapzen)
library(rgdal)
library(ggplot2)
library(scales)
library(nycflights13)
library(readxl)
```

#TRAVELTIME; install this in R console (NOT R STUDIO)!!!
#Install the latest version of this package by entering the following in R:
#install.packages("remotes")
#remotes::install_github("tlorusso/traveltimeR")

```{r}
#install.packages("remotes")
#remotes::install_github("tlorusso/traveltimeR")
```



#getting population and maps of surrounding of page from acs
#I registered for my personal key from the website

##############
#travel time, I did this once to generate center RDS file
#to get the api and the id I visited the website and signed up:
#https://traveltime.com/docs/api/overview/getting-keys

```{r}
YourAPIKey <- "7bbbad489d637c38b2bea80e1e413721"
YourAppId <- "c1fae682"

```


#Error Check
```{r eval=FALSE, include=FALSE}
# retrieve data via request 

# The following transport modes are supported:

# "cycling"", "cycling_ferry", "driving", "driving+train", "driving_ferry", "public_transport", 
# "walking", "walking+coach", "walking_bus", "walking_ferry" or "walking_train".

# how far can you go by public transport within 30 minutes?



traveltime30 <- traveltime_map(appId="YourAppId",
               apiKey="YourAPIKey",
               location=c(47.378610,8.54000),
               traveltime=1800,
               type="public_transport",
               departure="2018-11-15T08:00:00+01:00")

# ... and within 60 minutes?
traveltime60 <- traveltime_map(appId="YourAppId",
               apiKey="YourAPIKey",
               location=c(47.378610,8.54000),
               traveltime=3600,
               type="public_transport",
               departure="2018-11-15T08:00:00+01:00")

```


# Checks: latitude, Longitude, seconds
# Also, departure time must lie in the future.

```{r}
# retrieve data via request 

# The following transport modes are supported:

# "cycling"", "cycling_ferry", "driving", "driving+train", "driving_ferry", "public_transport", 
# "walking", "walking+coach", "walking_bus", "walking_ferry" or "walking_train".

# how far can you go by public transport within 30 minutes?



traveltime30 <- traveltime_map(appId=YourAppId,
               apiKey=YourAPIKey,
               location=c(47.378610,8.54000),
               traveltime=1800,
               type="driving",
               departure="2022-07-06T08:00:00+01:00")

# ... and within 60 minutes?
traveltime60 <- traveltime_map(appId=YourAppId,
              apiKey=YourAPIKey,
              location=c(47.378610,8.54000),
              traveltime=3600,
              type="driving",
              departure="2022-07-06T08:00:00+01:00")

```





View the polygons
```{r}
#traveltime30
#traveltime60
```



```{r}
m1 = mapview(traveltime60,  col.regions = c("grey"))
# add the second layer on top
m1 + traveltime30
```


# Check on leaflet map, this needs editing
```{r eval=FALSE, include=FALSE}
mypalette <- colorNumeric(palette="viridis", centerPop_RPK_dist$POPULATION)

map <- leaflet() %>%
  addTiles() %>%
  addProviderTiles("Esri") %>%  addPolygons(data=RPK_dist_outline,color = mypalette(centerPop_RPK_dist$POPULATION),
              smoothFactor = 0.2, fillOpacity=.6, weight = 1,stroke = F, 
              label=paste(" ", acs_RPK_dist$Census_tract,", Population: ",centerPop_RPK_dist$POPULATION))
              
%>%
  
###Adding the travel time bounds
   addPolygons(data = traveltime30 , color = "green",
               opacity = 1, weight = 2, fillColor = "white",fillOpacity = .1, group = "zurich driving distance")              
              
map              
```




# Useful link

[Website](https://tlorusso.github.io/traveltime/vignette.html#:~:text=traveltime%20%2D%20a%20Traveltime%20API%20Wrapper%20for%20R,-1%20Querying%20the&text=The%20isochrones%20display%20how%20far,modes%20of%20transport%20are%20supported.&text=For%20non%2Dcommercial%20use%20the,max%2030%20queries%20per%20min)