---
title: "Futher processing for EVI"
author: "Frankie Fan"
date: '2022-06-28'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(readxl)
library(dplyr)
library(tidyverse)
library(sf)
library(ggplot2)
library(rgdal)
library(sp)
library(leaflet)
library(directlabels)

library(ggrepel)
```

## Info for EVI:

Pixel: 463.313 meters\
Satellite: MODIS\
generated from the MODIS/006/MOD09GA surface reflectance composites


### read in the files

```{r, echo=FALSE, include=FALSE}
EVI_monthly <- read_csv("./Data/EVI_monthly.csv")
AnnualEVI <- read_csv("./Data/EVI_annual.csv")
zim_district <- st_read("./Shapefiles/Zim_D60.shp")  
EVI_long <- read_csv("./Data/EVI_long.csv") 
zim_region <- st_read("./Shapefiles/agro-ecological-regions.shp")

```


```{r, echo=FALSE, include=FALSE}
# Rename cols to match
zim_district <- rename(zim_district, District = NAME_2)
```


```{r, echo=FALSE, include=FALSE}
zim_district <- zim_district %>% 
  select(District)

MonthlyEVIbyDis <-full_join (zim_district, `EVI_monthly`, by = "District")
```

## 1. Monthly map for Year 2011 and 2017
```{r, echo=FALSE}
# Maximum evi by month
MaxMonthlyEVI2011 <- MonthlyEVIbyDis %>% 
  filter(Year == 2011) %>% 
  arrange(Month) %>% 
  ggplot() +
  geom_sf(size = 0.1, color = "black", aes(fill = MaxEVI)) +
  coord_sf() +
  scale_fill_viridis_c(option = "G", direction = -1) +
  facet_wrap(~Month) +
  ggtitle("Max EVI in Zimbabwe - 2011")
MaxMonthlyEVI2011



MaxMonthlyEVI2017 <- MonthlyEVIbyDis %>% 
  filter(Year == 2017) %>% 
  arrange(Month) %>% 
  ggplot() +
  geom_sf(size = 0.1, color = "black", aes(fill = MaxEVI)) +
  coord_sf() +
  scale_fill_viridis_c(option = "G", direction = -1) +
  facet_wrap(~Month) +
  ggtitle("Max EVI in Zimbabwe - 2017")
MaxMonthlyEVI2017
```
The two maps above show the spatial visualization of maximum EVI of each month by district. We could see that the maximum EVI (deepest blue) of a year occurs in February and March, and this is coherent with the weather and the growing seasons of crops in Zim--the rainy season is from November to March, and the earliest harvest time could be in April. 


## 2a. Distribution of EVI from 2011-2017

```{r, echo=FALSE}

EVI_long %>% 
  filter(Year == 2011|Year == 2012|Year == 2013|Year == 2014|Year == 2015|Year == 2016|Year == 2017) %>% 
  ggplot(aes(x = Year, y = EVI, fill = as.factor(Year))) + 
  geom_boxplot() +
  stat_summary(fun = "mean", geom = "point", shape = 8,
               size = 2, color = "white") +
  scale_fill_brewer(palette="Set1", name = "Year") +
  labs(title = "Distribution of EVI in Zimbabwe, Year 2011-2017") 

```
Here I used the white star '*' to represent the average EVI in a year, as it presents an overall summary of the EVI by year. However, the median (the black line in the middle of a bar) could be a better indicator when there is a regional drought in Zimbabwe.


## 2b. Distribution of EVI in 2011 and 2017
```{r, echo=FALSE}
AnnualEVI %>% 
  filter( Year == 2011|Year == 2017) %>% 
  gather(Type, EVI, AverageEVI:MedianEVI) %>% 
  ggplot(aes(x = Type, y = EVI, fill = Type)) +
  scale_fill_brewer(palette="Set3", name = "Type") +
  facet_wrap(~Year)+
  geom_boxplot() +
  labs(title = "Distribution of EVI, Year 2011 & 2017") +
    xlab("Statistics") +
    ylab("EVI")

```


## 3. map for EVI in March in 2011 and 2017

```{r, visualization for March, echo=FALSE}

MaxMarch <- MonthlyEVIbyDis %>% 
  filter(Year == 2011|Year == 2017, Month == "03") %>% 
  ggplot() +
  geom_sf(size = 0.1, color = "black", aes(fill = MaxEVI)) +
  facet_wrap(~Year) +
  coord_sf() +
  scale_fill_viridis_c(option = "G", direction = -1) +
  ggtitle("Maximum EVI in Zimbabwe - March")
MaxMarch
```
The map shows a comparison of the maximum EVI between Year 2011 and 2017. Here I chose March (the month with max EVI in a year) as it will compare the EVI in two years in the same scale. It is obvious that March 2017 has a higher in almost all districts. 



```{r}

### Selected Years

EVISelectedYears <- EVI_monthly %>% 
  filter(Month == "05"|Month == "04"|Month =="03"|Month =="02"|Month =="01"|Month =="10"|Month =="11"|Month =="12", 
         Year == 2010|Year == 2011|Year == 2016|Year == 2017) %>% 
  filter(!(Year == 2010 & Month == "03")) %>% 
  filter(!(Year == 2010 & Month == "04")) %>%
  filter(!(Year == 2010 & Month == "05")) %>%
  filter(!(Year == 2010 & Month == "02")) %>% 
  filter(!(Year == 2010 & Month == "01")) %>% 
  filter(!(Year == 2011 & Month == "10")) %>% 
  filter(!(Year == 2011 & Month == "11")) %>%
  filter(!(Year == 2011 & Month == "12")) %>% 
  
  filter(!(Year == 2016 & Month == "03")) %>% 
  filter(!(Year == 2016 & Month == "04")) %>%
  filter(!(Year == 2016 & Month == "05")) %>%
  filter(!(Year == 2016 & Month == "02")) %>% 
  filter(!(Year == 2016 & Month == "01")) %>%
  filter(!(Year == 2017 & Month == "10")) %>% 
  filter(!(Year == 2017 & Month == "11")) %>%
  filter(!(Year == 2017 & Month == "12")) %>% 
  mutate(GrowingSeason = if_else(Year == 2010|Year==2011, "2011", "2017"))
  
EVISelectedYears$YM <- paste(EVISelectedYears$Year, EVISelectedYears$Month, sep="-")


EVI2011 <- EVI_monthly %>% 
  filter(Month == "05"|Month == "04"|Month =="03"|Month =="02"|Month =="01"|Month =="10"|Month =="11"|Month =="12", 
         Year == 2010|Year == 2011) %>% 
  filter(!(Year == 2010 & Month == "03")) %>% 
  filter(!(Year == 2010 & Month == "04")) %>%
  filter(!(Year == 2010 & Month == "05")) %>%
  filter(!(Year == 2010 & Month == "02")) %>% 
  filter(!(Year == 2010 & Month == "01")) %>% 
  filter(!(Year == 2011 & Month == "10")) %>% 
  filter(!(Year == 2011 & Month == "11")) %>%
  filter(!(Year == 2011 & Month == "12"))
EVI2011$YM <- paste(EVI2011$Year, EVI2011$Month, sep="-")

EVI2017 <- EVI_monthly %>% 
  filter(Month == "05"|Month == "04"|Month =="03"|Month =="02"|Month =="01"|Month =="10"|Month =="11"|Month =="12", 
         Year == 2016|Year == 2017) %>% 
  filter(!(Year == 2016 & Month == "03")) %>% 
  filter(!(Year == 2016 & Month == "04")) %>%
  filter(!(Year == 2016 & Month == "05")) %>%
  filter(!(Year == 2016 & Month == "02")) %>% 
  filter(!(Year == 2016 & Month == "01")) %>%
  filter(!(Year == 2017 & Month == "10")) %>% 
  filter(!(Year == 2017 & Month == "11")) %>%
  filter(!(Year == 2017 & Month == "12"))
EVI2017$YM <- paste(EVI2017$Year, EVI2017$Month, sep="-")
```


## Time Series Scatter Plot

```{r}
`2011&2017` <- EVISelectedYears %>% 
  filter(District == "Hwange") %>% 
  ggplot(aes(x = YM, y = MaxEVI)) +
  geom_line(aes(group=1, color = as.factor(GrowingSeason)))+
  geom_point() +
  theme(axis.text.x = element_text(angle = 315)) +
  labs(title = "Maximum EVI in Hwange During Growing Season--2011 & 2017", color =  "Growing Season")+
  xlab("Time")+
  ylab("Maximum EVI")


Beitbridge <- EVISelectedYears %>% 
  filter(District == "Beitbridge") %>% 
  ggplot(aes(x = YM, y = MaxEVI)) +
  geom_line(aes(group=1, color = as.factor(GrowingSeason)))+
  geom_point() +
  theme(axis.text.x = element_text(angle = 315)) +
  labs(title = "Maximum EVI in Beitbridge During Growing Season--2011 & 2017", color =  "Growing Season")+
  xlab("Time")+
  ylab("Maximum EVI")



badVis <- EVISelectedYears %>% 
  ggplot(aes(x = YM, y = MaxEVI)) +
  geom_line(aes(group=1), color = "blue")+
  geom_point(aes(color = factor(District))) +
  theme(axis.text.x = element_text(angle = 315)) +
  labs(title = "Maximum EVI During Growing Season--2011 & 2017")+
  xlab("Time")+
  ylab("Maximum EVI")


`2011&2017`
Beitbridge
badVis
```
Here I chose the district "Hwange", and plotted a graph to show the variation in its EVI across the growing seasons in 2011 and 2017.\

We could see from the graph that the EVI peaks at Feb/March, and has it lowest values in October. This lines up with the farming season--the land is cleared for sowing in October, and the harvest is usually during Apr/May, so the crops are still in land in Feb/March. 

\
This would only show one district in Zim because having 60 districts add another layer to the graph, which could be very unclear for visualization if trying to graph them all at once (see `badVis`).


## Spatial Visulization

```{r, echo=FALSE, include=FALSE}
zim_district <- rename(zim_district, District = NAME_2) %>% 
  select(District)

zim_region <- rename(zim_region, Region = nat_region) %>% 
  select(Region)

GrowingSsonEVIbyDis2017 <-full_join (zim_district, `EVI2017`, by = "District")
GrowingSsonEVIbyDis2011 <-full_join (zim_district, `EVI2011`, by = "District")
```
## 4. Spatial Visualization for growing seasons 2011&2017
```{r}
GrowEVI2011 <- GrowingSsonEVIbyDis2011 %>% 
    mutate(GSOrder = case_when(Month =="10" ~ "1", 
                             Month =="11" ~ "2",
                             Month =="12" ~ "3",
                             Month =="01" ~ "4",
                             Month =="02" ~ "5",
                             Month =="03" ~ "6",
                             Month =="04" ~ "7",
                             Month =="05" ~ "8"))
                             
GrowEVI2011$Month[which(GrowEVI2011$Month=="10")] <- "October"
GrowEVI2011$Month[which(GrowEVI2011$Month=="11")] <- "November"
GrowEVI2011$Month[which(GrowEVI2011$Month=="12")] <- "December"
GrowEVI2011$Month[which(GrowEVI2011$Month=="01")] <- "January"
GrowEVI2011$Month[which(GrowEVI2011$Month=="02")] <- "Febuary"
GrowEVI2011$Month[which(GrowEVI2011$Month=="03")] <- "March"
GrowEVI2011$Month[which(GrowEVI2011$Month=="04")] <- "April"
GrowEVI2011$Month[which(GrowEVI2011$Month=="05")] <- "May"

GrowEVI2011$Month <- reorder(GrowEVI2011$Month, as.numeric(GrowEVI2011$GSOrder))
GrowEVI2011$Month <- as.factor(GrowEVI2011$Month)


GrowEVI2011 %>% 
  ggplot() +
  geom_sf(size = 0.1, color = "black", aes(fill = MaxEVI)) +
  coord_sf() +
  scale_fill_viridis_c(option = "G", direction = -1) +
  facet_wrap(~Month) +
  ggtitle("Max EVI in Zimbabwe - Growing Seaon 2011")



GrowEVI2017 <- GrowingSsonEVIbyDis2017 %>%
  mutate(GSOrder = case_when(Month =="10" ~ "1", 
                             Month =="11" ~ "2",
                             Month =="12" ~ "3",
                             Month =="01" ~ "4",
                             Month =="02" ~ "5",
                             Month =="03" ~ "6",
                             Month =="04" ~ "7",
                             Month =="05" ~ "8"))
                             
GrowEVI2017$Month[which(GrowEVI2017$Month=="10")] <- "October"
GrowEVI2017$Month[which(GrowEVI2017$Month=="11")] <- "November"
GrowEVI2017$Month[which(GrowEVI2017$Month=="12")] <- "December"
GrowEVI2017$Month[which(GrowEVI2017$Month=="01")] <- "January"
GrowEVI2017$Month[which(GrowEVI2017$Month=="02")] <- "Febuary"
GrowEVI2017$Month[which(GrowEVI2017$Month=="03")] <- "March"
GrowEVI2017$Month[which(GrowEVI2017$Month=="04")] <- "April"
GrowEVI2017$Month[which(GrowEVI2017$Month=="05")] <- "May"

GrowEVI2017$Month <- reorder(GrowEVI2017$Month, as.numeric(GrowEVI2017$GSOrder))
GrowEVI2017$Month <- as.factor(GrowEVI2017$Month)

GrowEVI2017 %>% 
  ggplot() +
  geom_sf(size = 0.1, color = "black", aes(fill = MaxEVI)) +
  coord_sf() +
  scale_fill_viridis_c(option = "G", direction = -1) +
  facet_wrap(~Month) +
  ggtitle("Max EVI in Zimbabwe - Growing Seaon 2017")

GrowEVI2011
GrowEVI2017
```
The EVI partially matches up with the growing season in Zim--sowing in Oct, but it seems that in May there isnt that much lost. 


## Leaflet (Not Ready Yet)

```{r}

# Notes for adding layer--DONT RUN

addTiles(group = "OSM (default)") %>%
  addProviderTiles(providers$Stamen.Toner, group = "Toner") %>%
  addProviderTiles(providers$Stamen.TonerLite, group = "Toner Lite") %>%
  # Overlay groups
  addCircles(~long, ~lat, ~10^mag/5, stroke = F, group = "Quakes") %>%
  addPolygons(data = outline, lng = ~long, lat = ~lat,
    fill = F, weight = 2, color = "#FFFFCC", group = "Outline") %>%
  # Layers control
  addLayersControl(
    baseGroups = c("OSM (default)", "Toner", "Toner Lite"),
    overlayGroups = c("Quakes", "Outline"),
    options = layersControlOptions(collapsed = FALSE)
  )
```

```{r, Leaflet for GrowingSeason2011}
mypal <- colorNumeric(
  palette = "viridis",
  domain = GrowingSsonEVIbyDis2011$MaxEVI)
mypal(c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6))

#Flip the direction of scale of color
# labFormat = labelFormat(transform = function(MaxEVI) sort(MaxEVI, decreasing = TRUE))

leaflet(GrowingSsonEVIbyDis2011) %>%
  addTiles() %>% 
  addPolygons(color = ~mypal(MaxEVI), weight = 1, smoothFactor = 0.5, label = ~MaxEVI,
    opacity = 1.0, fillOpacity = 0.5,
    highlightOptions = highlightOptions(color = "white", weight = 2,
      bringToFront = TRUE)) %>% 
  addLegend( labFormat = labelFormat(transform = function(MaxEVI) sort(MaxEVI, decreasing = TRUE)),
    position = "bottomleft",
    pal = mypal,
    values = GrowingSsonEVIbyDis2011$MaxEVI,
    title = "Max EVI in Zimbabwe - Growing Seaon 2011")
```




## Leaflet--Map w/ 15 layers 



## 5. Static Map--Average Max EVI for every district from 2011-2017
```{r}
EVI_MAX <- EVI_long %>% 
  group_by(District, Year) %>% 
  summarise(MaxEVI = max(EVI, na.rm = TRUE)) %>% 
  group_by(District) %>% 
  summarise(AvgAnnualMaxEVI = mean(MaxEVI, na.rm = TRUE))

AvrgAnnualMaxEVI <- full_join(zim_district, EVI_MAX, by = "District")

StaticMap <- AvrgAnnualMaxEVI %>% 
  ggplot() +
  geom_sf(size = 0.15, color = "black", aes(fill = AvgAnnualMaxEVI)) +
  coord_sf() +
  scale_fill_viridis_c(option = "G", direction = -1) +
  ggtitle("Average Annual Maximum EVI in Zimbabwe")




PRECIPmonthly <- read_csv("./Data/PRECIP_filtered.csv")
PRECIPAvg <- PRECIPmonthly %>% 
  group_by(District, Year) %>% 
  summarise(MeanEVI = mean(Precipitation, na.rm = TRUE)) %>% 
  group_by(District) %>% 
  summarise(AvgAnnualEVI = mean(MeanEVI, na.rm = TRUE))
AvrgAnnualPRECIP <- full_join(zim_district, PRECIPAvg, by = "District")


Map2 <- AvrgAnnualPRECIP %>% 
  ggplot() +
  geom_sf(size = 0.15, color = "black", aes(fill = AvgAnnualEVI)) +
  coord_sf() +
  scale_fill_viridis_c(option = "G", direction = -1) +
  ggtitle("Average Annual Precipitation in Zimbabwe")

StaticMap
Map2
```
## Data Cleaning for EVI by Region
```{r}
EVI_region_source<- read_csv("./Data/EVI_ts_Zimb_region.csv")

```
1. Drop some unessential columns 
```{r}
#This is in wide format
EVI_region_wide <- EVI_region_source %>% 
  select(nat_region, `2005_03_01_EVI`:`2021_12_30_EVI`) %>% #select needed columns--Districts and observations
  rename(Region = nat_region) #rename column
```

2. Transform it to long format
```{r}
# Parsed through the date with "_". Might need to change the code when it comes with different format
# Here the format for observation is yyyy_mm_dd_NDVI. Modify it if your observation comes with a different format.
EVI_region_long <- gather(EVI_region_wide, Date, EVI, `2005_03_01_EVI`:`2021_12_30_EVI`)%>% 
  separate( col=Date, into=c('Year', 'Month', "Day", "EVI11"), sep='_') %>% # Parsed it into Year/Month/Day
  select(-EVI11) #drop the _NDVI string segment

EVI_region_processed <-  EVI_region_long %>% 
  group_by(Region, Year, Month) %>%   # Group by district, year and month
  summarise(AverageEVI = mean(EVI, na.rm=TRUE),   # Find the mean, max, min by district
         MaxEVI = max(EVI, na.rm=TRUE),
         MinEVI = min(EVI, na.rm=TRUE),
         MedianEVI = median(EVI, na.rm=TRUE))

# write.csv(EVI_region_long,"./Data/EVI_region_long.csv", row.names = FALSE)
# write.csv(EVI_region_processed,"./Data/EVI_region_processed.csv", row.names = FALSE)
```

## 6. Spatial Visualization: Average Annual MaxEVI by Region
```{r}
EVI_MAX_region <- EVI_region_long %>% 
  group_by(Region, Year) %>% 
  summarise(MaxEVI = max(EVI, na.rm = TRUE)) %>% 
  group_by(Region) %>% 
  summarise(AvgAnnualMaxEVI = mean(MaxEVI, na.rm = TRUE))

AvrgAnnualMaxEVI_region <- full_join(zim_region, EVI_MAX_region, by = "Region")

StaticMapSet2 <- AvrgAnnualMaxEVI_region %>% 
  ggplot() +
  geom_sf(size = 0.15, color = "black", aes(fill = AvgAnnualMaxEVI)) +
  coord_sf() +
  scale_fill_viridis_c(option = "G", direction = -1) +
  ggtitle("Average Annual Maximum EVI in Zimbabwe")

StaticMapSet2


# Just do feb and march for each year, and average for year



```
## 7. Line graph: Time Series Line Graph for MAX EVI 

```{r}
EVIGrSs3 <- EVI_region_long %>% 
  filter(Month == "05"|Month == "04"|Month =="03"|Month =="02"|Month =="01"|Month =="10"|Month =="11"|Month =="12", 
         Year == 2005:2021) %>% 
  filter(!(Year == 2005 & Month == "03")) %>% 
  filter(!(Year == 2005 & Month == "04")) %>%
  filter(!(Year == 2005 & Month == "05")) %>%
  filter(!(Year == 2005 & Month == "02")) %>% 
  filter(!(Year == 2005 & Month == "01")) %>% 
  filter(!(Year == 2021 & Month == "10")) %>% 
  filter(!(Year == 2021 & Month == "11")) %>%
  filter(!(Year == 2021 & Month == "12")) %>% 
  group_by(Region, Month) %>% 
  summarise(AverageEVI = mean(EVI, na.rm = TRUE),
            MaxEVI = max(EVI, na.rm = TRUE)) %>% 
  mutate(GSOrder = case_when(Month =="10" ~ "1", 
                             Month =="11" ~ "2",
                             Month =="12" ~ "3",
                             Month =="01" ~ "4",
                             Month =="02" ~ "5",
                             Month =="03" ~ "6",
                             Month =="04" ~ "7",
                             Month =="05" ~ "8"))
                             
EVIGrSs3$Month[which(EVIGrSs3$Month=="10")] <- "October"
EVIGrSs3$Month[which(EVIGrSs3$Month=="11")] <- "November"
EVIGrSs3$Month[which(EVIGrSs3$Month=="12")] <- "December"
EVIGrSs3$Month[which(EVIGrSs3$Month=="01")] <- "January"
EVIGrSs3$Month[which(EVIGrSs3$Month=="02")] <- "Febuary"
EVIGrSs3$Month[which(EVIGrSs3$Month=="03")] <- "March"
EVIGrSs3$Month[which(EVIGrSs3$Month=="04")] <- "April"
EVIGrSs3$Month[which(EVIGrSs3$Month=="05")] <- "May"

EVIGrSs3$Month <- reorder(EVIGrSs3$Month, as.numeric(EVIGrSs3$GSOrder))
EVIGrSs3$Month <- as.factor(EVIGrSs3$Month)
EVIGrSs3$Region <- as.factor(EVIGrSs3$Region)

# Average EVI
EVIGrSs3 %>% 
  ggplot(aes(x = Month, y = AverageEVI, group = as.factor(Region), color = as.factor(Region))) +
  geom_line()+
  theme(axis.text.x = element_text(angle = 315)) +
  scale_colour_discrete(guide = 'none') +
  scale_x_discrete(expand=c(0, 1)) +
  geom_dl(aes(label = Region), method = list(dl.combine("first.points", "last.points")), cex = 0.8) +
  scale_color_viridis_d(option = "H") +
  labs(title = "Average EVI in Zim During Growing Season--By Month", color =  "Region") +
  xlab("Time(Month)") +
  ylab("Average EVI") 

# This is the same line graph, with a trend line and the actual data points
EVIGrSs3 %>%
  ggplot(aes(x = Month, y = AverageEVI, group = as.factor(Region), color = as.factor(Region))) +
  geom_line(alpha = I(7/10), color="grey", show.legend=F) +
  #stat_smooth(size=2, span=0.3, se=F, show_guide=F)
  geom_point(size=1) +
  geom_smooth(se=FALSE)+
  geom_text(aes( label = Region))


# Do average over maximum

# Max EVI
EVIGrSs3 %>% 
  ggplot(aes(x = Month, y = MaxEVI, group = as.factor(Region), color = as.factor(Region))) +
  geom_line()+
  theme(axis.text.x = element_text(angle = 315)) +
  scale_colour_discrete(guide = 'none') +
  scale_x_discrete(expand=c(0, 1)) +
  geom_dl(aes(label = Region), method = list(dl.combine("first.points", "last.points")), cex = 0.8) +
  scale_color_viridis_d(option = "H") +
  labs(title = "Max EVI in Zim During Growing Season--By Month", color =  "Region") +
  xlab("Time(Month)") +
  ylab("Max EVI") 


```
## Zim Region Map
```{r}
RegionMap <- zim_region %>% 
  ggplot() +
  geom_sf(size = 0.15, color = "black", aes(fill = Region)) +
  coord_sf() +
  scale_fill_viridis_d(option = "H") +
  theme(legend.title = element_text(size = 10), 
               legend.text = element_text(size = 10)) +
  labs(title = "Agro-ecological regions in Zimbabwe", color =  "Agro-ecological regions")

RegionMap
```

