---
title: "MPI_2017"
author: "Ari"
date: '2022-06-21'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


###This Script will be used to read In MPI data from 2011 & 2017 

Imports 
```{r}
library(readxl)
library(dplyr)
library(tidyverse)
library(sf)
library(ggplot2)
library(rgdal)
library(ggsn)
library(grid)
```

read in the MPI Excel
```{r}
MPI_2017 <- read_excel("./2017_MPI_excerpt data.xlsx")
```

```{r}
head(MPI_2017)
```

Import Shape file into r (Change district 91 --> district 61)
```{r}
#file name: 0=boundary, 1=province, 2=district 
zim_boundary <- st_read("./shape60/gadm36_ZWE_0.shp") 
zim_province <- st_read("./shape60/gadm36_ZWE_1.shp")
zim_district <- st_read("./shape60/gadm36_ZWE_2.shp")  
```
plot boundary, province, district 
```{r}
plot(zim_boundary)
plot(zim_province)
plot(zim_district)

```
Rename cols to match
```{r}
zim_district <- rename(zim_district, District_name = "NAME_2")
```


Get the IDs to match 
```{r}
zim_district <- zim_district %>% 
  arrange(District_name) %>% 
  mutate(District_ID = c(1:60))

joined_zim <-  full_join (zim_district,MPI_2017, by = "District_ID")
  
```

 
Mapping M0_k3
Adjusted Headcount Ratio -  The simple headcount ratio is simply the number of individuals considered to be poor divided by the entire population. 

```{r}
ggplot() +
geom_sf(data = joined_zim, size = 1, color = "black", aes(fill = M0_k3)) +
ggtitle("Adjusted Headcount Ratio in Zimbabwe - 2017") + guides(fill=guide_legend(title="AHR (M0_k3)")) + 
scale_fill_viridis_c(breaks = c(0.00, 0.05, 0.10, 0.15, 0.20, 0.25, 0.30, 0.35, 0.40), option = "plasma", direction = -1)+
coord_sf() + 
north(joined_zim, symbol = 15, scale = 0.10, location = "topleft") + 
scalebar(joined_zim, location = "topleft", dist = 100, st.size = 3 , height = 0.02, transform = TRUE, model = "WGS84", dist_unit = "km")
```

Mapping M1_k3 
Adjusted Poverty Gap -  The simple headcount ratio is simply the number of individuals considered to be poor divided by the entire population

```{r}
ggplot() +
  geom_sf(data = joined_zim, size = 1, color = "black", aes(fill = M1_k3)) +
  coord_sf()+ 
  scale_fill_viridis_c(breaks = c(0.00, 0.05, 0.10, 0.15, 0.20, 0.25, 0.30, 0.35, 0.40), option = "inferno", direction = -1) +
  ggtitle("Adjusted Poverty Gap in Zimbabwe - 2017") + guides(fill=guide_legend(title="APG (M1_k3)"))  + 
north(joined_zim, symbol = 15, scale = 0.10, location = "topleft") + 
scalebar(joined_zim, location = "topleft", dist = 100, st.size = 3 , height = 0.02, transform = TRUE, model = "WGS84", dist_unit = "km")

```

Mapping M2_k3 
Adjusted Poverty Severity - This is simply the square of the distance between a poor individual and the poverty threshold,  k .
```{r}
ggplot() +
geom_sf(data = joined_zim, size = 1, color = "black", aes(fill = M2_k3)) +
ggtitle("Adjusted Poverty Severity in Zimbabwe - 2017")+ guides(fill=guide_legend(title="APS (M2_k3)")) + 
scale_fill_viridis_b(breaks = c(0.00, 0.05, 0.10, 0.15, 0.20, 0.25, 0.30, 0.35, 0.40), option = "E", direction = -1) +
coord_sf() + 
north(joined_zim, symbol = 15, scale = 0.10, location = "topleft") + 
scalebar(joined_zim, location = "topleft", dist = 100, st.size = 3 , height = 0.02, transform = TRUE, model = "WGS84", dist_unit = "km")

```

Horizontal Bar Chart - M0_k3 Adjusted Headcount Ratio
```{r}
joined_zim %>% 
  arrange(desc(M0_k3))  %>% 
  ggplot(aes(x=reorder(District_name.x , M0_k3), y = M0_k3, fill = M0_k3)) +
  geom_bar(stat="identity") + coord_flip() + labs(title="Plot of Adjusted Headcount Ratio per District", 
         x="District Name", y = "Adjusted HeadCount Ratio") + theme(axis.text.y = element_text(size = 6)) + guides(fill=guide_legend(title="AHR")) + scale_fill_viridis_c(breaks = c(0.00, 0.05, 0.10, 0.15, 0.20, 0.25, 0.30, 0.35, 0.40), option = "plasma", direction = -1)
```
Horizontal Bar Chart - M1_k3 Adjusted Poverty Gap
```{r}

joined_zim %>% 
  arrange(desc(M1_k3))  %>%
  ggplot(aes(x=reorder(District_name.x , M1_k3), y = M1_k3, fill = M1_k3)) +
  geom_bar(stat="identity") + coord_flip() + labs(title="Plot of Adjusted Poverty Gap per District", 
         x="District Name", y = "Adjusted Poverty Gap") + theme(axis.text.y = element_text(size = 6)) + guides(fill=guide_legend(title="APG")) + scale_fill_viridis_c(breaks = c(0.00, 0.05, 0.10, 0.15, 0.20, 0.25, 0.30, 0.35, 0.40), option = "inferno", direction = -1)

```




Horizontal Bar Chart - M2_k3 Adjusted Poverty Severity
```{r}

joined_zim %>% 
  arrange(desc(M2_k3))  %>%
  ggplot(aes(x=reorder(District_name.x , M2_k3), y = M2_k3, fill = M2_k3)) +
  geom_bar(stat="identity") + coord_flip() + labs(title="Plot of Adjusted Poverty Severity per District", 
         x="District Name", y = "Adjusted Poverty Severity") + theme(axis.text.y = element_text(size = 6)) + guides(fill=guide_legend(title="APS")) + scale_fill_viridis_c(breaks = c(0.00, 0.05, 0.10, 0.15, 0.20, 0.25, 0.30, 0.35, 0.40), option = "E", direction = -1)

```
```{r}
#plot(joined_zim["M0_k3"]) 

#ggplot(data = joined_zim) + geom_sf(aes(fill= "M0_k3", geometry = "geometry")) 
#ggplot(data = joined_zim)+ geom_polygon(aes(alpha = 50), x= "District_ID", y = "District_name.x", fill = "M0_k3")



#ggplot() +
#geom_sf(data = joined_zim, size = 1, color = "black", aes(fill=M0_k3)) +
#ggtitle("Population at Severe Risk of Food Insecurity in Niger - 2015") + scale_fill_viridis_c()+
#coord_sf()

#class(joined_zim)


  
#plot(joined_zim, col= joined_zim$M0_k3, bg="skyblue", lwd=0.25,ylim = c(0,50), xlim = c(0,50))

#zim_2011 <- st_read(joined_zim)

#plot(joined_zim['M0_k3'])
#plot(joined_zim)

#mapping_m0 <- plot(joined_zim, )

```
map m0
```{r}
#ggplot() +
#(data = joined_zim, size = 1, color = "black", aes(fill=M0_k3)) +
#ggtitle("adjusted headcount ratio 2017") + scale_fill_viridis_c()+
#coord_sf()
```
map m1
```{r}
#tmp <- getOtmp <- getOption("ggplot2.continuous.fill") # store current setting
#options(ggplot2.continuous.fill = scale_fill_continuous(type = "tmp <- getOption("ggplot2.continuous.fill") # store current setting
#options(ggplot2.continuous.fill = scale_fill_continuous(type = "",breaks= c(0.00,0.05,0.10,0.15,0.20,0.25,0.30,0.35,0.40)))
#ggplot() +
#geom_sf(data = joined_zim, size = 1, color = "black", aes(fill=M1_k3)) +
#ggtitle("adjusted poverty gap 2017") + scale_fill_viridis_c()+
#coord_sf()
```
map m2
```{r}
#ggplot() +
#geom_sf(data = joined_zim, size = 1, color = "black", aes(fill=M2_k3)) +
#ggtitle("adjusted poverty gap squared 2017") + scale_fill_viridis_c()+
#coord_sf()
```


