---
title: "EVI-Cleaned"
author: "Frankie Fan"
date: '2022-07-11'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(readxl)
library(dplyr)
library(tidyverse)
library(sf)
library(ggplot2)
library(rgdal)
library(sp)
library(directlabels)

library(ggrepel)
```

## Info for EVI:

Pixel: 463.313 meters\
Satellite: MODIS\
generated from the MODIS/006/MOD09GA surface reflectance composites



## 1. 

Generate mean and standard deviation of monthly EVI for 2010-11 and 2016-17 growing seasons by region (these will only be included in Leaflet as a pop-up when the cursor is placed on a specific region)

```{r, echo=FALSE, include=FALSE}
# I uploaded them in my `Data` folder under `Frankie's Branch`

GrSs2011 <- read_csv("./Data/EVI_region_GrSs2011.csv")
GrSs2017 <- read_csv("./Data/EVI_region_GrSs2017.csv")


# Other Files
zim_district <- st_read("./Shapefiles/Zim_D60.shp")  
zim_region <- st_read("./Shapefiles/agro-ecological-regions.shp")
EVI_region_long <- read_csv("./Data/EVI_region_long.csv")

```



## 2.

Time series graphs by region of maximum monthly EVI for 2010-11 and 2016-17 growing seasons (note: these will be two separate graphs)

```{r}
GrSs2011Line <- EVI_region_long %>% 
  filter(Month == "05"|Month == "04"|Month =="03"|Month =="02"|Month =="01"|Month =="10"|Month =="11"|Month =="12", 
         Year == 2010|Year == 2011) %>% 
  filter(!(Year == 2010 & Month == "03")) %>% 
  filter(!(Year == 2010 & Month == "04")) %>%
  filter(!(Year == 2010 & Month == "05")) %>%
  filter(!(Year == 2010 & Month == "02")) %>% 
  filter(!(Year == 2010 & Month == "01")) %>% 
  filter(!(Year == 2011 & Month == "10")) %>% 
  filter(!(Year == 2011 & Month == "11")) %>%
  filter(!(Year == 2011 & Month == "12")) %>% 
  group_by(Region, Month) %>% 
  summarise(MaxEVI = max(EVI, na.rm = TRUE)) %>% 
  mutate(GSOrder = case_when(Month =="10" ~ "1", 
                             Month =="11" ~ "2",
                             Month =="12" ~ "3",
                             Month =="01" ~ "4",
                             Month =="02" ~ "5",
                             Month =="03" ~ "6",
                             Month =="04" ~ "7",
                             Month =="05" ~ "8"))
                             
GrSs2011Line$Month[which(GrSs2011Line$Month=="10")] <- "October"
GrSs2011Line$Month[which(GrSs2011Line$Month=="11")] <- "November"
GrSs2011Line$Month[which(GrSs2011Line$Month=="12")] <- "December"
GrSs2011Line$Month[which(GrSs2011Line$Month=="01")] <- "January"
GrSs2011Line$Month[which(GrSs2011Line$Month=="02")] <- "Febuary"
GrSs2011Line$Month[which(GrSs2011Line$Month=="03")] <- "March"
GrSs2011Line$Month[which(GrSs2011Line$Month=="04")] <- "April"
GrSs2011Line$Month[which(GrSs2011Line$Month=="05")] <- "May"

GrSs2011Line$Month <- reorder(GrSs2011Line$Month, as.numeric(GrSs2011Line$GSOrder))
GrSs2011Line$Month <- as.factor(GrSs2011Line$Month)
GrSs2011Line$Region <- as.factor(GrSs2011Line$Region)


# Max EVI
GrSs2011Line %>% 
  ggplot(aes(x = Month, y = MaxEVI, group = as.factor(Region), color = as.factor(Region))) +
  geom_line()+
  theme(axis.text.x = element_text(angle = 315)) +
  scale_colour_discrete(guide = 'none') +
  scale_x_discrete(expand=c(0, 1)) +
  geom_dl(aes(label = Region), method = list(dl.combine("first.points", "last.points")), cex = 0.8) +
  scale_color_viridis_d(option = "H") +
  labs(title = "Max EVI in Zim During Growing Season 2011", color =  "Region") +
  xlab("Time(Month)") +
  ylab("Max EVI") 

```


```{r}
GrSs2017Line <- EVI_region_long %>% 
  filter(Month == "05"|Month == "04"|Month =="03"|Month =="02"|Month =="01"|Month =="10"|Month =="11"|Month =="12", 
         Year == 2016|Year == 2017) %>% 
  filter(!(Year == 2016 & Month == "03")) %>% 
  filter(!(Year == 2016 & Month == "04")) %>%
  filter(!(Year == 2016 & Month == "05")) %>%
  filter(!(Year == 2016 & Month == "02")) %>% 
  filter(!(Year == 2016 & Month == "01")) %>% 
  filter(!(Year == 2017 & Month == "10")) %>% 
  filter(!(Year == 2017 & Month == "11")) %>%
  filter(!(Year == 2017 & Month == "12")) %>% 
  group_by(Region, Month) %>% 
  summarise(MaxEVI = max(EVI, na.rm = TRUE)) %>% 
  mutate(GSOrder = case_when(Month =="10" ~ "1", 
                             Month =="11" ~ "2",
                             Month =="12" ~ "3",
                             Month =="01" ~ "4",
                             Month =="02" ~ "5",
                             Month =="03" ~ "6",
                             Month =="04" ~ "7",
                             Month =="05" ~ "8"))
                             
GrSs2017Line$Month[which(GrSs2017Line$Month=="10")] <- "October"
GrSs2017Line$Month[which(GrSs2017Line$Month=="11")] <- "November"
GrSs2017Line$Month[which(GrSs2017Line$Month=="12")] <- "December"
GrSs2017Line$Month[which(GrSs2017Line$Month=="01")] <- "January"
GrSs2017Line$Month[which(GrSs2017Line$Month=="02")] <- "Febuary"
GrSs2017Line$Month[which(GrSs2017Line$Month=="03")] <- "March"
GrSs2017Line$Month[which(GrSs2017Line$Month=="04")] <- "April"
GrSs2017Line$Month[which(GrSs2017Line$Month=="05")] <- "May"

GrSs2017Line$Month <- reorder(GrSs2017Line$Month, as.numeric(GrSs2017Line$GSOrder))
GrSs2017Line$Month <- as.factor(GrSs2017Line$Month)
GrSs2017Line$Region <- as.factor(GrSs2017Line$Region)


# Max EVI
GrSs2017Line %>% 
  ggplot(aes(x = Month, y = MaxEVI, group = as.factor(Region), color = as.factor(Region))) +
  geom_line()+
  theme(axis.text.x = element_text(angle = 315)) +
  scale_colour_discrete(guide = 'none') +
  scale_x_discrete(expand=c(0, 1)) +
  geom_dl(aes(label = Region), method = list(dl.combine("first.points", "last.points")), cex = 0.8) +
  scale_color_viridis_d(option = "H") +
  labs(title = "Max EVI in Zim During Growing Season 2017", color =  "Region") +
  xlab("Time(Month)") +
  ylab("Max EVI") 

```


##3. 

Spatial maps of max EVI during the 2010-11 and 2016-17 growing seasons by region (note: these will be two separate graphs

```{r}
# Regional 2011

# Max

EVIGrow2011 <- full_join(zim_region, GrSs2011, by = "Region")

RgMaxEVI2011 <- EVIGrow2011 %>% 
  ggplot() +
  geom_sf(size = 0.15, color = "black", aes(fill = MaxEVI)) +
  coord_sf() +
  scale_fill_viridis_c(option = "G", direction = -1) +
  ggtitle("Maximum EVI in Zimbabwe-Growing Season 2011")

RgMaxEVI2011
```


```{r}
# Regional 2017

# Max

EVIGrow2017 <- full_join(zim_region, GrSs2017, by = "Region")

RgMaxEVI2017 <- EVIGrow2011 %>% 
  ggplot() +
  geom_sf(size = 0.15, color = "black", aes(fill = MaxEVI)) +
  coord_sf() +
  scale_fill_viridis_c(option = "G", direction = -1) +
  ggtitle("Maximum EVI in Zimbabwe-Growing Season 2017")

RgMaxEVI2017
```


## Zim Region Map
```{r}
RegionMap <- zim_region %>% 
  ggplot() +
  geom_sf(size = 0.15, color = "black", aes(fill = Region)) +
  coord_sf() +
  scale_fill_viridis_d(option = "H") +
  theme(legend.title = element_text(size = 10), 
               legend.text = element_text(size = 10)) +
  labs(title = "Agro-ecological regions in Zimbabwe", color =  "Agro-ecological regions")

RegionMap
```

