---
title: "Futher processing for EVI"
author: "Frankie Fan"
date: '2022-06-28'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(readxl)
library(dplyr)
library(tidyverse)
library(sf)
library(ggplot2)
library(rgdal)
library(sp)
library(leaflet)
library(directlabels)
```

## Info for EVI:

Pixel: 463.313 meters\
Satellite: MODIS\
generated from the MODIS/006/MOD09GA surface reflectance composites


### read in the files

```{r, echo=FALSE, include=FALSE}
EVI_monthly <- read_csv("./Data/EVI_monthly.csv")
AnnualEVI <- read_csv("./Data/EVI_annual.csv")
zim_district <- st_read("./Shapefiles/Zim_D60.shp")  
EVI_long <- read_csv("./Data/EVI_long.csv") 
zim_region <- st_read("./Shapefiles/agro-ecological-regions.shp")

```

### Selected Years
```{r}
EVISelectedYears <- EVI_monthly %>% 
  filter(Month == "05"|Month == "04"|Month =="03"|Month =="02"|Month =="01"|Month =="10"|Month =="11"|Month =="12", 
         Year == 2010|Year == 2011|Year == 2016|Year == 2017) %>% 
  filter(!(Year == 2010 & Month == "03")) %>% 
  filter(!(Year == 2010 & Month == "04")) %>%
  filter(!(Year == 2010 & Month == "05")) %>%
  filter(!(Year == 2010 & Month == "02")) %>% 
  filter(!(Year == 2010 & Month == "01")) %>% 
  filter(!(Year == 2011 & Month == "10")) %>% 
  filter(!(Year == 2011 & Month == "11")) %>%
  filter(!(Year == 2011 & Month == "12")) %>% 
  
  filter(!(Year == 2016 & Month == "03")) %>% 
  filter(!(Year == 2016 & Month == "04")) %>%
  filter(!(Year == 2016 & Month == "05")) %>%
  filter(!(Year == 2016 & Month == "02")) %>% 
  filter(!(Year == 2016 & Month == "01")) %>%
  filter(!(Year == 2017 & Month == "10")) %>% 
  filter(!(Year == 2017 & Month == "11")) %>%
  filter(!(Year == 2017 & Month == "12")) %>% 
  mutate(GrowingSeason = if_else(Year == 2010|Year==2011, "2011", "2017"))
  
EVISelectedYears$YM <- paste(EVISelectedYears$Year, EVISelectedYears$Month, sep="-")


EVI2011 <- EVI_monthly %>% 
  filter(Month == "05"|Month == "04"|Month =="03"|Month =="02"|Month =="01"|Month =="10"|Month =="11"|Month =="12", 
         Year == 2010|Year == 2011) %>% 
  filter(!(Year == 2010 & Month == "03")) %>% 
  filter(!(Year == 2010 & Month == "04")) %>%
  filter(!(Year == 2010 & Month == "05")) %>%
  filter(!(Year == 2010 & Month == "02")) %>% 
  filter(!(Year == 2010 & Month == "01")) %>% 
  filter(!(Year == 2011 & Month == "10")) %>% 
  filter(!(Year == 2011 & Month == "11")) %>%
  filter(!(Year == 2011 & Month == "12"))
EVI2011$YM <- paste(EVI2011$Year, EVI2011$Month, sep="-")

EVI2017 <- EVI_monthly %>% 
  filter(Month == "05"|Month == "04"|Month =="03"|Month =="02"|Month =="01"|Month =="10"|Month =="11"|Month =="12", 
         Year == 2016|Year == 2017) %>% 
  filter(!(Year == 2016 & Month == "03")) %>% 
  filter(!(Year == 2016 & Month == "04")) %>%
  filter(!(Year == 2016 & Month == "05")) %>%
  filter(!(Year == 2016 & Month == "02")) %>% 
  filter(!(Year == 2016 & Month == "01")) %>%
  filter(!(Year == 2017 & Month == "10")) %>% 
  filter(!(Year == 2017 & Month == "11")) %>%
  filter(!(Year == 2017 & Month == "12"))
EVI2017$YM <- paste(EVI2017$Year, EVI2017$Month, sep="-")
```



## Time Series Scatter Plot

```{r}
`2011&2017` <- EVISelectedYears %>% 
  filter(District == "Hwange") %>% 
  ggplot(aes(x = YM, y = MaxEVI)) +
  geom_line(aes(group=1, color = as.factor(GrowingSeason)))+
  geom_point() +
  theme(axis.text.x = element_text(angle = 315)) +
  labs(title = "Maximum EVI in Hwange During Growing Season--2011 & 2017", color =  "Growing Season")+
  xlab("Time")+
  ylab("Maximum EVI")


Beitbridge <- EVISelectedYears %>% 
  filter(District == "Beitbridge") %>% 
  ggplot(aes(x = YM, y = MaxEVI)) +
  geom_line(aes(group=1, color = as.factor(GrowingSeason)))+
  geom_point() +
  theme(axis.text.x = element_text(angle = 315)) +
  labs(title = "Maximum EVI in Beitbridge During Growing Season--2011 & 2017", color =  "Growing Season")+
  xlab("Time")+
  ylab("Maximum EVI")



badVis <- EVISelectedYears %>% 
  ggplot(aes(x = YM, y = MaxEVI)) +
  geom_line(aes(group=1), color = "blue")+
  geom_point(aes(color = factor(District))) +
  theme(axis.text.x = element_text(angle = 315)) +
  labs(title = "Maximum EVI During Growing Season--2011 & 2017")+
  xlab("Time")+
  ylab("Maximum EVI")


MaxEVI2011 <- EVI2011 %>% 
  filter(District == "Hwange") %>% 
  ggplot(aes(x = YM, y = MaxEVI)) +
  geom_line(aes(group=1), color = "blue")+
  geom_point() +
  theme(axis.text.x = element_text(angle = 315)) +
  labs(title = "Maximum EVI in Hwange During Growing Season--2011")+
  xlab("Time")+
  ylab("Maximum EVI")


MaxEVI2017 <- EVI2017 %>% 
  filter(District == "Hwange") %>% 
  ggplot(aes(x = YM, y = MaxEVI)) +
  geom_line(aes(group=1), color = "blue")+
  geom_point() +
  theme(axis.text.x = element_text(angle = 315)) +
  labs(title = "Maximum EVI in Hwange During Growing Season--2017")+
  xlab("Time")+
  ylab("Maximum EVI")

`2011&2017`
Beitbridge
MaxEVI2011
MaxEVI2017
badVis
```
Here I chose the district "Hwange", and plotted a graph to show the variation in its EVI across the growing seasons in 2011 and 2017.\

We could see from the graph that the EVI peaks at Feb/March, and has it lowest values in October. This lines up with the farming season--the land is cleared for sowing in October, and the harvest is usually during Apr/May, so the crops are still in land in Feb/March. 

\
This would only show one district in Zim because having 60 districts add another layer to the graph, which could be very unclear for visualization if trying to graph them all at once (see `badVis`).


## Spatial Visulization

```{r, echo=FALSE, include=FALSE}
zim_district <- rename(zim_district, District = NAME_2) %>% 
  select(District)

zim_region <- rename(zim_region, Region = nat_region) %>% 
  select(Region)

GrowingSsonEVIbyDis2017 <-full_join (zim_district, `EVI2017`, by = "District")
GrowingSsonEVIbyDis2011 <-full_join (zim_district, `EVI2011`, by = "District")
```

```{r}
GrowEVI2011 <- GrowingSsonEVIbyDis2011 %>% 
  ggplot() +
  geom_sf(size = 0.1, color = "black", aes(fill = MaxEVI)) +
  coord_sf() +
  scale_fill_viridis_c(option = "G", direction = -1) +
  facet_wrap(~Month) +
  ggtitle("Max EVI in Zimbabwe - Growing Seaon 2011")


GrowEVI2017 <- GrowingSsonEVIbyDis2017 %>% 
  ggplot() +
  geom_sf(size = 0.1, color = "black", aes(fill = MaxEVI)) +
  coord_sf() +
  scale_fill_viridis_c(option = "G", direction = -1) +
  facet_wrap(~Month) +
  ggtitle("Max EVI in Zimbabwe - Growing Seaon 2017")

GrowEVI2011
GrowEVI2017
```
The EVI partially matches up with the growing season in Zim--sowing in Oct, but it seems that in May there isnt that much lost. 


## Leaflet

```{r}

# Notes for adding layer--DONT RUN

addTiles(group = "OSM (default)") %>%
  addProviderTiles(providers$Stamen.Toner, group = "Toner") %>%
  addProviderTiles(providers$Stamen.TonerLite, group = "Toner Lite") %>%
  # Overlay groups
  addCircles(~long, ~lat, ~10^mag/5, stroke = F, group = "Quakes") %>%
  addPolygons(data = outline, lng = ~long, lat = ~lat,
    fill = F, weight = 2, color = "#FFFFCC", group = "Outline") %>%
  # Layers control
  addLayersControl(
    baseGroups = c("OSM (default)", "Toner", "Toner Lite"),
    overlayGroups = c("Quakes", "Outline"),
    options = layersControlOptions(collapsed = FALSE)
  )
```






```{r, Leaflet for GrowingSeason2011}
mypal <- colorNumeric(
  palette = "viridis",
  domain = GrowingSsonEVIbyDis2011$MaxEVI)
mypal(c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6))

#Flip the direction of scale of color
# labFormat = labelFormat(transform = function(MaxEVI) sort(MaxEVI, decreasing = TRUE))

leaflet(GrowingSsonEVIbyDis2011) %>%
  addTiles() %>% 
  addPolygons(color = ~mypal(MaxEVI), weight = 1, smoothFactor = 0.5, label = ~MaxEVI,
    opacity = 1.0, fillOpacity = 0.5,
    highlightOptions = highlightOptions(color = "white", weight = 2,
      bringToFront = TRUE)) %>% 
  addLegend( labFormat = labelFormat(transform = function(MaxEVI) sort(MaxEVI, decreasing = TRUE)),
    position = "bottomleft",
    pal = mypal,
    values = GrowingSsonEVIbyDis2011$MaxEVI,
    title = "Max EVI in Zimbabwe - Growing Seaon 2011")
```






## z Score
```{r}
EVI_long$Year <- as.numeric(EVI_long$Year)
EVI_long$Month <- as.numeric(EVI_long$Month)
EVI_long$Day <- as.numeric(EVI_long$Day)


MaxEVIGrow <- EVI_long %>% 
  filter(Month == 1:5|Month == 10:12) %>% 
  filter(!(Year == 2005 & Month == 3)) %>% 
  filter(!(Year == 2005 & Month == 4)) %>%
  filter(!(Year == 2005 & Month == 5)) %>%
  filter(!(Year == 2005 & Month == 2)) %>% 
  filter(!(Year == 2005 & Month == 1)) %>% 
  
  filter(!(Year == 2021 & Month == 10)) %>% 
  filter(!(Year == 2021 & Month == 11)) %>%
  filter(!(Year == 2021 & Month == 12)) %>% 
  mutate(YMD = paste(Year, Month, Day, sep="-")) %>% 
  group_by(District, Year, Month) %>% 
  summarise( 
         MaxEVI = max(EVI, na.rm=TRUE))


MaxEVIPop <- MaxEVIGrow %>% 
  group_by(District, Year, Month) %>% 
  summarise(sdMaxEVI = sd(MaxEVI, na.rm=TRUE),
         MeanMaxEVI = max(MaxEVI, na.rm=TRUE))
  
  
  

PopMeanEVIMax = mean(as.numeric(MaxEVI), na.rm = TRUE)
  
```



## Leaflet--Map w/ 15 layers 



## Static Map-- Max EVI for every district
```{r}
EVI_MAX <- EVI_long %>% 
  group_by(District, Year) %>% 
  summarise(MaxEVI = max(EVI, na.rm = TRUE)) %>% 
  group_by(District) %>% 
  summarise(AvgAnnualMaxEVI = mean(MaxEVI, na.rm = TRUE))

AvrgAnnualMaxEVI <- full_join(zim_district, EVI_MAX, by = "District")

StaticMap <- AvrgAnnualMaxEVI %>% 
  ggplot() +
  geom_sf(size = 0.15, color = "black", aes(fill = AvgAnnualMaxEVI)) +
  coord_sf() +
  scale_fill_viridis_c(option = "G", direction = -1) +
  ggtitle("Average Annual Maximum EVI in Zimbabwe")




PRECIPmonthly <- read_csv("./Data/PRECIP_filtered.csv")
PRECIPAvg <- PRECIPmonthly %>% 
  group_by(District, Year) %>% 
  summarise(MeanEVI = mean(Precipitation, na.rm = TRUE)) %>% 
  group_by(District) %>% 
  summarise(AvgAnnualEVI = mean(MeanEVI, na.rm = TRUE))
AvrgAnnualPRECIP <- full_join(zim_district, PRECIPAvg, by = "District")


Map2 <- AvrgAnnualPRECIP %>% 
  ggplot() +
  geom_sf(size = 0.15, color = "black", aes(fill = AvgAnnualEVI)) +
  coord_sf() +
  scale_fill_viridis_c(option = "G", direction = -1) +
  ggtitle("Average Annual Precipitation in Zimbabwe")

StaticMap
Map2
```

```{r}
EVI_region_source<- read_csv("./Data/EVI_ts_Zimb_region.csv")

```
1. Drop some unessential columns 
```{r}
#This is in wide format
EVI_region_wide <- EVI_region_source %>% 
  select(nat_region, `2005_03_01_EVI`:`2021_12_30_EVI`) %>% #select needed columns--Districts and observations
  rename(Region = nat_region) #rename column
```

2. Transform it to long format
```{r}
# Parsed through the date with "_". Might need to change the code when it comes with different format
# Here the format for observation is yyyy_mm_dd_NDVI. Modify it if your observation comes with a different format.
EVI_region_long <- gather(EVI_region_wide, Date, EVI, `2005_03_01_EVI`:`2021_12_30_EVI`)%>% 
  separate( col=Date, into=c('Year', 'Month', "Day", "EVI11"), sep='_') %>% # Parsed it into Year/Month/Day
  select(-EVI11) #drop the _NDVI string segment

EVI_region_processed <-  EVI_region_long %>% 
  group_by(Region, Year, Month) %>%   # Group by district, year and month
  summarise(AverageEVI = mean(EVI, na.rm=TRUE),   # Find the mean, max, min by district
         MaxEVI = max(EVI, na.rm=TRUE),
         MinEVI = min(EVI, na.rm=TRUE),
         MedianEVI = median(EVI, na.rm=TRUE))

write.csv(EVI_region_long,"./Data/EVI_region_long.csv", row.names = FALSE)
write.csv(EVI_region_processed,"./Data/EVI_region_processed.csv", row.names = FALSE)
```


```{r}
EVI_MAX_region <- EVI_region_long %>% 
  group_by(Region, Year) %>% 
  summarise(MaxEVI = max(EVI, na.rm = TRUE)) %>% 
  group_by(Region) %>% 
  summarise(AvgAnnualMaxEVI = mean(MaxEVI, na.rm = TRUE))

AvrgAnnualMaxEVI_region <- full_join(zim_region, EVI_MAX_region, by = "Region")

StaticMapSet2 <- AvrgAnnualMaxEVI_region %>% 
  ggplot() +
  geom_sf(size = 0.15, color = "black", aes(fill = AvgAnnualMaxEVI)) +
  coord_sf() +
  scale_fill_viridis_c(option = "G", direction = -1) +
  ggtitle("Average Annual Maximum EVI in Zimbabwe")

StaticMapSet2
```
## Time Series Line Graph for MAX EVI 
```{r}
# EVI in growing seasons by year by month
EVIGrSs <- EVI_region_long %>% 
  filter(Month == "05"|Month == "04"|Month =="03"|Month =="02"|Month =="01"|Month =="10"|Month =="11"|Month =="12", 
         Year == 2005:2021) %>% 
  filter(!(Year == 2005 & Month == "03")) %>% 
  filter(!(Year == 2005 & Month == "04")) %>%
  filter(!(Year == 2005 & Month == "05")) %>%
  filter(!(Year == 2005 & Month == "02")) %>% 
  filter(!(Year == 2005 & Month == "01")) %>% 
  filter(!(Year == 2021 & Month == "10")) %>% 
  filter(!(Year == 2021 & Month == "11")) %>%
  filter(!(Year == 2021 & Month == "12")) %>% 
  group_by(Region, Year, Month) %>% 
  summarise(MaxEVI = max(EVI, na.rm = TRUE))
 
  mutate(GrowingSeason = if_else(Year == 2010|Year==2011, "2011", "2017"))
  
EVIGrSs$YM <- paste(EVIGrSs$Year, EVIGrSs$Month, sep="-")


EVIGrSsTimeSeries <- EVIGrSs %>% 
  ggplot(aes(x = YM, y = MaxEVI)) +
  geom_line(aes(group=1, color = as.factor(Region)))+
  geom_point() +
  theme(axis.text.x = element_text(angle = 315)) +
  labs(title = "Maximum EVI in Zim During Growing Season", color =  "Region") +
  xlab("Time") +
  ylab("Maximum EVI")


EVIGrSsTimeSeries2 <- EVIGrSs %>% 
  ggplot(aes(x = YM, y = MaxEVI)) +
  geom_line(aes(group=1, color = as.factor(Region)))+
  geom_point() +
  theme(axis.text.x = element_text(angle = 315)) +
  facet_wrap(~Region) +
  labs(title = "Maximum EVI in Zim During Growing Season", color =  "Region") +
  xlab("Time") +
  ylab("Maximum EVI")

EVIGrSsTimeSeries2
EVIGrSsTimeSeries
```
```{r}
# EVI in growing seasons by year
EVIGrSs2 <- EVI_region_long %>% 
  filter(Month == "05"|Month == "04"|Month =="03"|Month =="02"|Month =="01"|Month =="10"|Month =="11"|Month =="12", 
         Year == 2005:2021) %>% 
  filter(!(Year == 2005 & Month == "03")) %>% 
  filter(!(Year == 2005 & Month == "04")) %>%
  filter(!(Year == 2005 & Month == "05")) %>%
  filter(!(Year == 2005 & Month == "02")) %>% 
  filter(!(Year == 2005 & Month == "01")) %>% 
  filter(!(Year == 2021 & Month == "10")) %>% 
  filter(!(Year == 2021 & Month == "11")) %>%
  filter(!(Year == 2021 & Month == "12")) %>% 
  group_by(Region, Year) %>% 
  summarise(MaxEVI = max(EVI, na.rm = TRUE))


EVIGrSsTimeSeriesByYear <- EVIGrSs2 %>% 
  ggplot(aes(x = Year, y = MaxEVI)) +
  geom_line(aes(group=1, color = as.factor(Region)))+
  geom_point(aes(color = Region, shape = Region)) +
  theme(axis.text.x = element_text(angle = 315)) +
  labs(title = "Maximum EVI in Zim During Growing Season--By Year", color =  "Region") +
  xlab("Time") +
  ylab("Maximum EVI")


EVIGrSsTimeSeriesByYear2 <- EVIGrSs2 %>% 
  ggplot(aes(x = Year, y = MaxEVI)) +
  geom_line(aes(group=1, color = as.factor(Region)))+
  geom_point(aes(shape = Region)) +
  theme(axis.text.x = element_text(angle = 315)) +
  facet_wrap(~Region)+
  labs(title = "Maximum EVI in Zim During Growing Season--By Year", color =  "Region") +
  xlab("Time") +
  ylab("Maximum EVI")
EVIGrSsTimeSeriesByYear2
EVIGrSsTimeSeriesByYear

EVIGrSsTimeSeries2017 <- EVIGrSs2 %>% 
  filter(Month == "05"|Month == "04"|Month =="03"|Month =="02"|Month =="01"|Month =="10"|Month =="11"|Month =="12", 
         Year == 2016:2017) %>% 
  filter(!(Year == 2016 & Month == "03")) %>% 
  filter(!(Year == 2016 & Month == "04")) %>%
  filter(!(Year == 2016 & Month == "05")) %>%
  filter(!(Year == 2016 & Month == "02")) %>% 
  filter(!(Year == 2016 & Month == "01")) %>% 
  filter(!(Year == 2017 & Month == "10")) %>% 
  filter(!(Year == 2017 & Month == "11")) %>%
  filter(!(Year == 2017 & Month == "12")) %>% 
  ggplot(aes(x = Year, y = MaxEVI)) +
  geom_line(aes(group=1, color = as.factor(Region)))+
  geom_point(aes(color = Region, shape = Region)) +
  theme(axis.text.x = element_text(angle = 315)) +
  labs(title = "Maximum EVI in Zim During Growing Season--By Year", color =  "Region") +
  xlab("Time") +
  ylab("Maximum EVI") 




```

## Time Series Line Graph for Average EVI by Month
```{r}
EVIGrSs3 <- EVI_region_long %>% 
  filter(Month == "05"|Month == "04"|Month =="03"|Month =="02"|Month =="01"|Month =="10"|Month =="11"|Month =="12", 
         Year == 2005:2021) %>% 
  filter(!(Year == 2005 & Month == "03")) %>% 
  filter(!(Year == 2005 & Month == "04")) %>%
  filter(!(Year == 2005 & Month == "05")) %>%
  filter(!(Year == 2005 & Month == "02")) %>% 
  filter(!(Year == 2005 & Month == "01")) %>% 
  filter(!(Year == 2021 & Month == "10")) %>% 
  filter(!(Year == 2021 & Month == "11")) %>%
  filter(!(Year == 2021 & Month == "12")) %>% 
  group_by(Region, Month) %>% 
  summarise(AverageEVI = mean(EVI, na.rm = TRUE)) %>% 
  mutate(GSOrder = case_when(Month =="10" ~ "1", 
                             Month =="11" ~ "2",
                             Month =="12" ~ "3",
                             Month =="01" ~ "4",
                             Month =="02" ~ "5",
                             Month =="03" ~ "6",
                             Month =="04" ~ "7",
                             Month =="05" ~ "8"))
                             


EVIGrSs3$Month[which(EVIGrSs3$Month=="10")] <- "October"
EVIGrSs3$Month[which(EVIGrSs3$Month=="11")] <- "November"
EVIGrSs3$Month[which(EVIGrSs3$Month=="12")] <- "December"
EVIGrSs3$Month[which(EVIGrSs3$Month=="01")] <- "January"
EVIGrSs3$Month[which(EVIGrSs3$Month=="02")] <- "Febuary"
EVIGrSs3$Month[which(EVIGrSs3$Month=="03")] <- "March"
EVIGrSs3$Month[which(EVIGrSs3$Month=="04")] <- "April"
EVIGrSs3$Month[which(EVIGrSs3$Month=="05")] <- "May"

EVIGrSs3$Month <- reorder(EVIGrSs3$Month, as.numeric(EVIGrSs3$GSOrder))
EVIGrSs3$Month <- as.factor(EVIGrSs3$Month)
EVIGrSs3$Region <- as.factor(EVIGrSs3$Region)
AvgEVIGrSsByMonth <- EVIGrSs3 %>% 
  ggplot(aes(x = Month, y = AverageEVI, group = as.factor(Region), color = as.factor(Region))) +
  geom_line()+
  geom_dl(aes(label = Region), method = list(dl.combine("first.points", "last.points")), cex = 0.8)+
  theme(axis.text.x = element_text(angle = 315)) +
  labs(title = "Average EVI in Zim During Growing Season--By Month", color =  "Region") +
  xlab("Time(Month)") +
  ylab("Average EVI") 

AvgEVIGrSsByMonth



EVIGrSs3 %>% 
  ggplot(aes(x = Month, y = AverageEVI, group = as.factor(Region), color = as.factor(Region))) +
  geom_line()+
  geom_text(aes(label = Region),
              hjust = 0, nudge_x = 0.1)+
  coord_cartesian(clip = "off") +
  theme(axis.text.x = element_text(angle = 315),
        legend.position = "none",
          plot.margin = margin(0.1, 2.6, 0.1, 0.1, "cm")) +
  labs(title = "Average EVI in Zim During Growing Season--By Month", color =  "Region") +
  xlab("Time(Month)") +
  ylab("Average EVI") 
```
## Zim Region Map
```{r}
RegionMap <- zim_region %>% 
  ggplot() +
  geom_sf(size = 0.15, color = "black", aes(fill = Region)) +
  coord_sf() +
  scale_fill_viridis_d(option = "H") +
  theme(legend.title = element_text(size = 10), 
               legend.text = element_text(size = 10)) +
  labs(title = "Agro-ecological regions in Zimbabwe", color =  "Agro-ecological regions")

RegionMap
```

